Regular singular Volterra equations on complex domains

### 2023-08-31 reg-sing-volterra.tex
Revise overview of {sec:image under soft_part}

        \item \textit{(Aaron)} State the desired result of Section~\ref{sec:image under soft_part}.

@@

Combining the arguments above, we learn that
\begin{align*}
\solproto & \in \zeta(b)^{-\tau}\,\zeta^{\tau-1}\;\Big[ B^{-1} + O\big(|\zeta|^{\epsilon}\big) \Big]\;e^{\eta(b)} \Big[1 + O\big(|\zeta|\big) \Big] \\
& = \zeta(b)^{-\tau} B^{-1} e^{\eta(b)}\;\zeta^{\tau-1} \Big[ 1 + O\big(|\zeta|^{\epsilon}\big) \Big] \Big[1 + O\big(|\zeta|\big) \Big] \\
& = M\zeta^{\tau-1} \Big[ 1 + O\big(|\zeta|^{\epsilon}\big) + O\big(|\zeta|\big) \Big]
\end{align*}
at $\zeta = 0$, with $M = \zeta(b)^{-\tau} B^{-1} e^{\eta(b)}$. Observing that $O\big(|\zeta|^{\epsilon}\big) + O\big(|\zeta|\big) = O\big(|\zeta|^{\epsilon'}\big)$, we get the desired result.
\end{proof}
\subsection{Showing that $\softpart$ makes the prototype solution less singular \\ \textit{(toward Theorem~\ref{thm:general_volterra})}}\label{sec:image under soft_part}

In this Section, we show that, under Condition \eqref{cond:eps-lambda}, the smoothing effect of the operator $\softpart$ regularizes the prototype solution $f_0$: recall from Section \ref{sec:asymptotics} that $\solproto \in \singexpalg{\tau-1}(\domain)$ \textcolor{MediumSpringGreen}{$\solproto\in\singexp{\tau-1}{\lambda_0}(\domain)$}, then we'll show $\softpart \solproto \in\singexpalg{\tau-1+\gamma}(\domain)$ \textcolor{MediumSpringGreen}{$\softpart \solproto \in\singexp{\tau-1+\gamma}{\Lambda}(\domain)$ for $\Lambda\geq \lambda_\Delta$}. This is a consequence of a more general result (see Proposition \ref{prop:smoothing}), namely that $\softpart$ regularises functions in $\singexp{\sigma}{\Lambda}(\Omega)$ which are not too singular at $\zeta=0$.

>>>>

        \item \textcolor{gray}{\textit{(Aaron)} State the desired result of Section~\ref{sec:image under soft_part}.}

@@

Combining the arguments above, we learn that
\begin{align*}
\solproto & \in \zeta(b)^{-\tau}\,\zeta^{\tau-1}\;\Big[ B^{-1} + O\big(|\zeta|^{\epsilon}\big) \Big]\;e^{\eta(b)} \Big[1 + O\big(|\zeta|\big) \Big] \\
& = \zeta(b)^{-\tau} B^{-1} e^{\eta(b)}\;\zeta^{\tau-1} \Big[ 1 + O\big(|\zeta|^{\epsilon}\big) \Big] \Big[1 + O\big(|\zeta|\big) \Big] \\
& = M\zeta^{\tau-1} \Big[ 1 + O\big(|\zeta|^{\epsilon}\big) + O\big(|\zeta|\big) \Big]
\end{align*}
at $\zeta = 0$, with $M = \zeta(b)^{-\tau} B^{-1} e^{\eta(b)}$. Observing that $O\big(|\zeta|^{\epsilon}\big) + O\big(|\zeta|\big) = O\big(|\zeta|^{\epsilon'}\big)$, we get the desired result.
\end{proof}
\subsection{Showing that $\softpart$ makes the prototype solution less singular \\ \textit{(toward Theorem~\ref{thm:general_volterra})}}\label{sec:image under soft_part}
Now that we know the prototype solution $\solproto$ belongs to $\singexpalg{\tau-1}(\domain)$, we'll show that $\softpart$ reduces the sharpness of its singularity at $\zeta = 0$, mapping it into $\singexpalg{\tau-1+\gamma}(\domain)$. This is a consequence of the general smoothing effect of $\softpart$, described in the following result.
\par\color{RoyalBlue}
In this Section, we show that, under Condition \eqref{cond:eps-lambda}, the smoothing effect of the operator $\softpart$ regularizes the prototype solution $f_0$: recall from Section \ref{sec:asymptotics} that $\solproto \in \singexpalg{\tau-1}(\domain)$ \textcolor{MediumSpringGreen}{$\solproto\in\singexp{\tau-1}{\lambda_0}(\domain)$}, then we'll show $\softpart \solproto \in\singexpalg{\tau-1+\gamma}(\domain)$ \textcolor{MediumSpringGreen}{$\softpart \solproto \in\singexp{\tau-1+\gamma}{\Lambda}(\domain)$ for $\Lambda\geq \lambda_\Delta$}. This is a consequence of a more general result (see Proposition \ref{prop:smoothing}), namely that $\softpart$ regularises functions in $\singexp{\sigma}{\Lambda}(\Omega)$ which are not too singular at $\zeta=0$.\color{black}
